Spatial Reasoning and Statistical Graphics

### 2014-10-05 Paper/Draft1/TestingVisualAptitude.Rnw
Fixing formatting/refs
Pictures updated with all data

\documentclass{article}
%---------------------------------------------------
\usepackage{color}
\usepackage[dvipsnames,svgnames]{xcolor}
\usepackage{wrapfig,float}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{url}
\usepackage{ulem}
\usepackage[section]{placeins}
\usepackage{sidecap}
\usepackage{multirow}
\usepackage{bbm}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage{rotating}

@@

<<VisReasoningAnalysis,echo=FALSE, include=FALSE, fig.width=8,fig.height=4>>=
lineup.summary$variable <- factor(lineup.summary$variable, labels=c("Video Game Hrs/Wk", "Card Rotation", "Figure Classification", "Paper Folding", "Visual Search"))
lineup.summary$variable <- factor(lineup.summary$variable, levels=c("Card Rotation", "Figure Classification", "Paper Folding", "Visual Search", "Video Game Hrs/Wk"))

@@

qplot(data=lineup.summary.categorical, x=value, y=lineup, geom="point", shape=I(1), size=I(3)) + facet_wrap(~variable, scales="free_x", ncol=3) + xlab("Value") + ylab("Lineup Score (# Correct - 1/19 # Incorrect)") + theme_bw()
ggsave(paste(imgdir, "fig-VisReasoningAnalysisCat.png", sep=""), width=6, height=6)
@

@@

>>>>

\documentclass{article}
%---------------------------------------------------
\usepackage{color}
\usepackage{fullpage}
\usepackage[dvipsnames,svgnames]{xcolor}
\usepackage{wrapfig,float}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{url}
\usepackage{ulem}
\usepackage[section]{placeins}
\usepackage{sidecap}
\usepackage{multirow}
\usepackage{bbm}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage{rotating}

@@

<<VisReasoningAnalysis,echo=FALSE, include=FALSE, fig.width=10,fig.height=5, out.width='\\linewidth'>>=
lineup.summary$variable <- factor(lineup.summary$variable, labels=c("Card Rotation", "Figure Classification", "Paper Folding", "Visual Search", "Log10 Video Game Hrs/Wk"))
lineup.summary$variable <- factor(lineup.summary$variable, levels=c("Card Rotation", "Figure Classification", "Paper Folding", "Visual Search", "Log10 Video Game Hrs/Wk"))

@@

qplot(data=lineup.summary.categorical, x=value, y=lineup, geom="boxplot") + facet_wrap(~variable, scales="free_x", ncol=3) + xlab("Value") + ylab("Lineup Score (# Correct - 1/19 # Incorrect)") + theme_bw() + geom_point(aes(x=value, y=lineup), shape=1, size=3)
ggsave(paste(imgdir, "fig-VisReasoningAnalysisCat.png", sep=""), width=6, height=6)
@

@@

\bibliography{references}
